CTA Proposal:\\SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe

### 2021-03-02 Phys 311/CTA/Paper/paper.tex
add paper
progress

\title{SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}

@@

When studying the early universe scientists commonly seek out stars with low metal content. Locked inside these stars
is information about the physical and chemical conditions that led to the formation of the star. The low metallicity of
these stars, specifically low [ Fe/H] values and high [$\alpha$/Fe] values, indicate that the stars were formed in the 
early universe. By comparing the quantity of $\alpha$-elements, iron, and hydrogen we can map the timescales of 
nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements are carbon, oxygen, neon, 
magnesium, silicon, sulfur, argon, and calcium.

@@

\section{Novelty} \label{sec:novelty}

The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the MIKE spectrograph focusing on 
the chemical enrichment process to better understand star formation in the very early universe. The six stars that were chosen 
were the brightest stars in SEGUE 1 which allowed for high resolution spectrography.

@@

Using the MIKE spectrograph the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, 
neutron-capture elements, and other lighter elements. The authors then compared this data to stars found in classical dSph 
galaxies and the Milky Way halo and concluded that SEGUE 1 is a surviving first galaxy with only one round of star formation. In
the three lowest metallicity stars, out of the six observed stars, the abundance of iron (both Fe I and Fe II) indistinguishable 
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing 
metallicity and increasing iron abundance. This indicated that there was only one Type Ia supernova that enriched SEGUE. This 
contrasts the trend found in galaxies from later where there would be a clear trend in increasing metallicity and increasing 
iron abundance as they evolve alongside energetic supernovae events. Other indications of the age of SEGUE include enhanced
[$\alpha$/Fe] values found in all it's stars that are consistent with their birth cloud, and the low abundance of neutron-capture
elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.

>>>>

\title{CTA Proposal:\\SEGUE 1: An Unevolved Fossil Galaxy from the Early Universe}

@@

When studying the early universe scientists commonly seek out stars with low metal content. Locked inside these stars
is information about the physical and chemical conditions that led to the formation of the star. The low metallicity of
these stars, specifically low [Fe/H] values and high [$\alpha$/Fe] values, indicate that the stars were formed in the
early universe. By comparing the quantity of $\alpha$-elements, iron, and hydrogen we can map the timescales of
nucleosynthesis to the timescales of different types of supernovae. The $\alpha$-elements that the authors are interested 
in are carbon, oxygen, neon, magnesium, silicon, sulfur, argon, and calcium.

@@

\section{Novelty and Methods} \label{sec:novelty}

The authors of this paper made new spectrography measurements of six stars within SEGUE 1 using the Magellan/MIKE and Keck/HIRES
spectrographs focusing on the chemical enrichment process to better understand star formation in the very early universe. The six
stars that were chosen were the brightest stars in SEGUE 1 which allowed for high resolution spectrography. Using the spectrographs
the authors collected data on the abundance of iron (Fe I and Fe II), carbon, $\alpha$-elements, neutron-capture elements, and other 
lighter elements. The authors then compared this data to stars found in classical dSph galaxies and the Milky Way halo.
The parameters for the measurements of each of the stars are listed in table 1. Due to the dim nature of the six starts the signal to
noise ratio (S/N) was only moderate with values between 20 and 50

@@

With the high resolution spectrograph data the authors were able to extrapolate the abundances of the various elements inside the stars.

In the three lowest metallicity stars, out of the six observed stars, the abundance of iron (both Fe I and Fe II) indistinguishable
from the noise in the measurements. In the 3 stars with observable amounts of iron there was no correlation between increasing
metallicity and increasing iron abundance. This indicated that there was only one Type Ia supernova that enriched SEGUE. This
contrasts the trend found in galaxies from later where there would be a clear trend in increasing metallicity and increasing
iron abundance as they evolve alongside energetic supernovae events. Other indications of the age of SEGUE include enhanced
[$\alpha$/Fe] values found in all it's stars that are consistent with their birth cloud, and the low abundance of neutron-capture
elements. The consistent [$\alpha$/Fe] values in SEGUE 1 stars suggest that there were no energetic supernovae events that enriched
the birth gas cloud during the star formation events. The low abundance of neutron-capture elements in SEGUE's non-binary stars,
which total to less than \(\sim 10^{-7} M_{\odot}\) for each element, indicate that there were no neutron-capture element producing
process, which produce \(\sim 10^{-4} M_{\odot}\) of neutron-capture elements per event, that occurred during the star formation phase.
